# `r paste(gsub("\\n$", "", rmarkdown::metadata$title), "- Supplementary Information")`


## Proportional hazards assumption


```{r pha-table, echo = FALSE}
pha <- cox.zph(rgcx)
rownames(pha$table)[match(names(rgcx.nms), rownames(pha$table))] <- rgcx.nms
knitr::kable(
    pha$table,
    digits = 2,
    col.names = c("Chi-square", "DF", "*p*-value"),
    caption = paste0(
        "Chi-square independence test between scaled Schoenfeld residuals ",
        "and time for each covariate ",
        "(as implemented by `cox.zph` in the *survival* package). ",
        "CVC, central venous catheters; DF, degree of freedom; ",
        "DVT, deep vein thrombosis; WBC1, white blood count on day one."
    )
)
```


```{r pha-plot, dev = ifelse_is_docx("pdf", "png"), echo = FALSE, fig.width = 12, fig.height = 12, fig.cap = "Scaled Schoenfeld residuals over transformed time for each covariate. Depicted *p*-values were calculated applying chi-square independence test. CVC, central venous catheters; DVT, deep vein thrombosis; WBC1, white blood count on day one."}
ggcoxzph(pha, df = 2)
```


## LOT numbers


```{r lottable, echo = FALSE}
lottbl <- cvc[c(
    "Id", "Manufacturer", "Type", "Lumens", "LOT", "PN", "isExcluded"
)]
lottbl$isExcluded <- factor(
    lottbl$isExcluded, levels = c(TRUE, FALSE), labels = c("yes", "no")
)
knitr::kable(
    lottbl,
    col.names = c(
        "Id", "MF", "Type", "LM", "LOT", "PN", "EX"
    ),
    caption = paste0(
        "LOT and part numbers of examined central venous catheters.",
        " EX: Excluded, LM: Lumens, MF: Manufacturer, PN: part number."
    )
)
```


## Catheter-related thrombosis size over time


```{r crtplots, include = FALSE}
.cmain <- function(main, col.main = rep(1, length(main)), ...) {
    n <- length(main)

    if (n != length(col.main))
        stop("'main' and 'col.main' have to have the same length.")

    p <- function(...)paste0(..., collapse = "")

    for (i in seq_along(main)) {
        left <- seq_len(i - 1)
        right <- i + seq_len(n - i)
        title(
            bquote(bold(
                phantom(.(p(main[left])))*.(main[i])*phantom(.(p(main[right])))
            )),
            col.main = col.main[i],
            ...
        )
    }
}
.crtplots <- function(x, col = mcol,
                      main = NULL, xlab = NULL, ylab = NULL, ...) {
    l <- reshape(
        x,
        idvar = "Id",
        timevar = "Day",
        v.names = "Size",
        varying = list(seq_len(ncol(x))[-(1:2)]),
        direction = "long"
    )

    # we screened on day 1, 3, 5, ...
    l$Day <- (2 * l$Day) - 1L

    old.par <- par(no.readonly = TRUE)
    on.exit(par(old.par))

    at.bp <- seq_len(ceiling(max(l$Day[!is.na(l$Size)]) / 2) * 6L)
    at.bp <- at.bp[as.logical(at.bp %% 6)]

    boxplot(
        Size ~ ManLu + Day,
        data = l,
        at = at.bp,
        col = paste0(col, "66"),
        pch = 20,
        frame = FALSE, xaxt = "n", yaxt = "n",
        main = NULL, xlab = NULL, ylab = NULL
    )
    beeswarm::beeswarm(
        Size ~ ManLu + Day,
        data = l,
        at = at.bp,
        add = TRUE,
        col = col,
        pch = 20
    )
    legend(
        "topright",
        legend = .manlu2txt(levels(l$ManLu)),
        col = col,
        pch = 20,
        bty = "n"
    )
    title(main = main, adj = 0L)
    title(xlab = xlab, adj = 0L, col.lab = "#808080")
    title(ylab = ylab, adj = 1L, col.lab = "#808080")
    axis(
        1L,
        at = seq(from = 2, to = tail(at.bp, 1), by = 6),
        labels = unique(l$Day[!is.na(l$Size)]),
        lwd.ticks = 0,
        col = "#808080"
    )
    axis(2L, col = "#808080", las = 2)
}
.crtovertime <- function(x, col, ylab) {
    l <- reshape(
        x,
        idvar = "Id",
        timevar = "Day",
        v.names = "Size",
        varying = list(seq_len(ncol(x))[-(1:2)]),
        direction = "long"
    )

    # we screened on day 1, 3, 5, ...
    l$Day <- (2 * l$Day) - 1L

    mday <- max(l$Day[!is.na(l$Size)])
    nl <- nlevels(l$ManLu)
    group <- as.numeric(l$ManLu)
    at <- ((group - 1) * (mday + nl + 1)) + l$Day
    l <- cbind(l, at)
    rng <- tapply(l$at, l$ManLu, range)

    plot(NA,
        xlim = range(at), ylim = c(0, max(l$Size, na.rm = TRUE)),
        frame = FALSE, xaxt = "n", yaxt = "n", ann = FALSE
    )
    points(at, l$Size, col = cols[l$ManLu], pch = 20, cex = 1.5)
    for (i in unique(l$Id)) {
        cur <- l[l$Id == i & !is.na(l$Size),]
        if (nrow(cur))
            arrows(
                cur$at[-nrow(cur)], cur$Size[-nrow(cur)],
                cur$at[-1], cur$Size[-1],
                col = paste0(cols[cur$ManLu], "80"),
                angle = 20, length = 0.1, lwd = 1.5
            )
    }

    for (i in seq(along = rng))
        lines(rng[[i]], c(0, 0), col = "#808080", lty = "dotted")
    text(
        x = vapply(rng, head, NA_real_, n = 1),
        y = 0,
        labels = "DAY 1",
        col = "#808080",
        adj = c(0, 1.5)
    )
    text(
        x = vapply(rng, tail, NA_real_, n = 1),
        y = 0,
        labels = paste0("DAY ", mday),
        col = "#808080",
        adj = c(1, 1.5)
    )
    text(
        x = vapply(rng, head, NA_real_, n = 1),
        y = 0,
        labels = names(rng),
        col = cols,
        adj = c(0, -0.5)
    )
    title(ylab = ylab, adj = 1L, col.lab = "#808080")
    axis(2L, col = "#808080", las = 2)
}
```


### Catheter-related thrombosis height


```{r crtheightbp, dev = ifelse_is_docx("pdf", "png"), fig.width = 15, fig.height = 10, echo = FALSE, fig.cap = "Boxplots of catheter-related thrombosis height over time."}
cols <- c(paste0("#115d", c("6e", "9e", "de")), mcol[2:3])
.crtplots(
    droplevels(cvc[!cvc$isExcluded, c("Id", "ManLu", paste0("Height", 1:17))]),
    col = cols,
    xlab = "DAY",
    ylab = "THROMBOSIS HEIGHT [mm]"
)
```


```{r crtheightovertime, dev = ifelse_is_docx("pdf", "png"), fig.width = 15, fig.height = 10, echo = FALSE, fig.cap = "Catheter-related thrombosis height over time."}
.crtovertime(
    droplevels(cvc[!cvc$isExcluded, c("Id", "ManLu", paste0("Height", 1:17))]),
    col = cols,
    ylab = "THROMBOSIS HEIGHT [mm]"
)
.cmain(
    c(
        "Catheter-related thrombosis height over time for ",
        "Arrow3", ", ", "Arrow4", ", ", "Arrow5", ", ",
        "Braun3", " and ", "Vygon5"
    ),
    c(
        "black",
        col[1], "black", cols[2], "black", cols[3], "black",
        col[4], "black", cols[5]
    ),
    adj = 0L
)
```


### Catheter-related thrombosis width


```{r crtwidthbp, dev = ifelse_is_docx("pdf", "png"), fig.width = 15, fig.height = 10, echo = FALSE, fig.cap = "Boxplots of catheter-related thrombosis width over time."}
.crtplots(
    droplevels(cvc[!cvc$isExcluded, c("Id", "ManLu", paste0("Width", 1:17))]),
    col = cols,
    xlab = "DAY",
    ylab = "THROMBOSIS WIDTH [mm]"
)
```


```{r crtwidthovertime, dev = ifelse_is_docx("pdf", "png"), fig.width = 15, fig.height = 10, echo = FALSE, fig.cap = "Catheter-related thrombosis width over time."}
.crtovertime(
    droplevels(cvc[!cvc$isExcluded, c("Id", "ManLu", paste0("Width", 1:17))]),
    col = cols,
    ylab = "THROMBOSIS WIDTH [mm]"
)
.cmain(
    c(
        "Catheter-related thrombosis width over time for ",
        "Arrow3", ", ", "Arrow4", ", ", "Arrow5", ", ",
        "Braun3", " and ", "Vygon5"
    ),
    c(
        "black",
        col[1], "black", cols[2], "black", cols[3], "black",
        col[4], "black", cols[5]
    ),
    adj = 0L
)
```


## Comparison CRT-free time


### Comparison CRT-free time Arrow5 vs Vygon5


```{r survplota5v5, echo = FALSE, dev = ifelse_is_docx("pdf", "png"), fig.width = 12, fig.height = 7, fig.cap = "Survival plot showing CRT-free time for five-lumen central venous catheters."}
xlim <- c(0.8, max(times))
mar <- c(0.1, 10.1, 1.1, 2.1)
nms <- .manlu2txt(gsub("ManLu=", "", names(m.a5v5$svf$strata)))
col <- c("#115dde", mcol["Vygon"])
names(col) <- nms

layout(matrix(1:3, nrow = 3), height = c(6, 1.0, 1.0))
par(mar = c(5.1, mar[-1]))
plot_surv(
    m.a5v5$svf,
    times = times,
    xlim = xlim,
    ylim = c(0, 1),
    mark.time = TRUE,
    conf.int = TRUE,
    col = col,
    lwd = 1,
    main = "Thrombus free time of CVCs",
    xlab = "time [days]"
)
legend(
    "topright",
    legend = c(nms, "95% confidence intervals"),
    col = c(col, "black"),
    lty = c("solid", "solid", "dotted"),
    lwd = 1, seg.len = 3, bty = "n"
)

.revcol <- function(x)x[, rev(seq_len(ncol(x)))]
nr <- drop(.nrisk(m.a5v5$svf))
nce <- drop(.ncumevents(m.a5v5$svf))
colnames(nr) <- colnames(nce) <- nms
nr <- .revcol(nr)
nce <- .revcol(nce)

par(mar = mar)
plot_table(
    nr, at = times, xlim = xlim,
    main = "Number at risk",
    xaxis = FALSE, cex.text = 1.5, col = col[colnames(nr)]
)
par(mar = mar)
plot_table(
    nce, at = times, xlim = xlim,
    main = "Cumulative number of events",
    xaxis = FALSE, cex.text = 1.5, col = col[colnames(nce)]
)
```


### Comparison CRT-free time Arrow4 vs Arrow5


```{r survplota4a5, echo = FALSE, dev = ifelse_is_docx("pdf", "png"), fig.width = 12, fig.height = 7, fig.cap = "Survival plot showing CRT-free time for four- and five-lumen central venous catheters."}
xlim <- c(0.8, max(times))
mar <- c(0.1, 10.1, 1.1, 2.1)
nms <- .manlu2txt(gsub("ManLu=", "", names(m.a4a5$svf$strata)))
col <- c(paste0("#115d", c("9e", "de")))
names(col) <- nms

layout(matrix(1:3, nrow = 3), height = c(6, 1.0, 1.0))
par(mar = c(5.1, mar[-1]))
plot_surv(
    m.a5v5$svf,
    times = times,
    xlim = xlim,
    ylim = c(0, 1),
    mark.time = TRUE,
    conf.int = TRUE,
    col = col,
    lwd = 1,
    main = "Thrombus free time of CVCs",
    xlab = "time [days]"
)
legend(
    "topright",
    legend = c(nms, "95% confidence intervals"),
    col = c(col, "black"),
    lty = c("solid", "solid", "dotted"),
    lwd = 1, seg.len = 3, bty = "n"
)

.revcol <- function(x)x[, rev(seq_len(ncol(x)))]
nr <- drop(.nrisk(m.a4a5$svf))
nce <- drop(.ncumevents(m.a4a5$svf))
colnames(nr) <- colnames(nce) <- nms
nr <- .revcol(nr)
nce <- .revcol(nce)

par(mar = mar)
plot_table(
    nr, at = times, xlim = xlim,
    main = "Number at risk",
    xaxis = FALSE, cex.text = 1.5, col = col[colnames(nr)]
)
par(mar = mar)
plot_table(
    nce, at = times, xlim = xlim,
    main = "Cumulative number of events",
    xaxis = FALSE, cex.text = 1.5, col = col[colnames(nce)]
)
```


## Hazard ratios


```{r supplhrtablefull, echo = FALSE, message = FALSE}
theme_gtsummary_journal()
theme_gtsummary_compact(font_size = 8L)

tbl_regression(
    rgcx.full,
    exponentiate = TRUE,
    label = list(
        ManLu ~ "Type (Manufacturer/Lumens)",
        DVT ~ "History of vein thrombosis",
        Experience ~ "Experience (number of CVCs in the past)",
        Attempts2 ~ "More than one insertion attempt",
        AdmissionType ~ "Admission type",
        PerioperativePlacement ~ "Placement in the OR",
        AnticoagulationGroup ~ "Type of anticoagulation drug",
        WBC1 ~ "WBC day 1 [Gpt/L]",
        DDimer1 ~ "D-dimer day 1 [mg/L]",
        CRP1 ~ "CRP day 1 [mg/L]"
    )) |>
    modify_caption(
        paste0(
            "Hazard ratios of CRT using all available variables ",
            "but with a reduced sample size of N=", rgcx.full$n,
            " central venous catheters due to missing values."
        )
    )
```


```{r forestplotfull, echo = FALSE, dev = ifelse_is_docx("pdf", "png"), fig.width = 12, fig.height = 12, fig.cap = "Hazard ratios for all available variables but with reduced sample size. CRP1: C-reactive peptide on day one; D-dimer1: d-dimer on day one; DVT, deep vein thrombosis; LMWH, low-molecular-weight heparins; UFH, unfractionated heparin; WBC1, white blood cell count on day one."}
.ggforest(
    rgcx.full,
    data = rd.na,
    labpos = c(0.1, 10),
    rename = c(
        ManLu = "Type",
        Attempts2 = "More than one attempt",
        DDimer1 = "D-dimer1",
        AdmissionType = "Admission type",
        PerioperativePlacement = "Perioperative placement",
        AnticoagulationGroup = "Anticoagulation"
    )
)
```


```{r supplhrtable, echo = FALSE, message = FALSE}
theme_gtsummary_journal()
theme_gtsummary_compact(font_size = 8L)

tbl_regression(
    rgcx,
    exponentiate = TRUE,
    label = list(
        ManLu ~ "Type (Manufacturer/Lumens)",
        DVT ~ "History of vein thrombosis",
        AdmissionType ~ "Admission type",
        PerioperativePlacement ~ "Placement in the OR",
        AnticoagulationGroup ~ "Type of anticoagulation drug",
        WBC1 ~ "WBC day 1 [Gpt/L]"
    )) |>
    modify_caption(
        paste0(
            "Hazard ratios for Cox regression of CRT for all analysed central venous catheters ",
            "(N=", rgcx$n, ")."
        )
    )
```


```{r supplhrtablelots, echo = FALSE, message = FALSE}
theme_gtsummary_journal()
theme_gtsummary_compact(font_size = 8L)

tbl_regression(
    rgcx.lots,
    exponentiate = TRUE,
    label = list(
        ManLu ~ "Type (Manufacturer/Lumens)",
        DVT ~ "History of vein thrombosis",
        AdmissionType ~ "Admission type",
        PerioperativePlacement ~ "Placement in the OR",
        AnticoagulationGroup ~ "Type of anticoagulation drug",
        WBC1 ~ "WBC day 1 [Gpt/L]"
    )) |>
    modify_caption(
        paste0(
            "Hazard ratios of CRT assuming that ",
            "central venous catheters with missing LOTs were of ",
            "each manufacturer's main type. ",
            "Sample size of N=", rgcx.lots$n, "."
        )
    )
```


```{r forestplotlots, echo = FALSE, dev = ifelse_is_docx("pdf", "png"), fig.width = 12, fig.height = 12, fig.cap = "Hazard ratios of CRT for all central venous catheters assuming that missing LOTs were of each manufacturer's main type. DVT, deep vein thrombosis; LMWH, low-molecular-weight heparins; UFH, unfractionated heparin; WBC1, white blood cell count on day one."}
.ggforest(
    rgcx.lots,
    data = rd.lots,
    rename = rgcx.nms
)
```


## R session information


```{r sessioninfo, echo = FALSE}
sessionInfo()
```

## Git commit hash


```{r gitcommithash, echo = FALSE}
sprintf("Git commit revision: %s", system("git rev-parse HEAD", intern = TRUE))
```
